\documentclass[line]{res}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
\usepackage[bottom = 0cm, top=2cm, left=2cm]{geometry}
\usepackage[pdftitle={Rebecca Meritz},
pdfauthor={Rebecca Meritz},
pdfsubject={Rebecca Meritz's \Resume},
pdfkeywords={Rebecca Meritz, \Resume, resume}]{hyperref}

\name{Rebecca J. Meritz}
\address{\hfill rebecca@meritz.com $\cdot$ (267)-559-3133 $\cdot$ github.com/rmeritz}

\begin{format}
\title{l}\dates{r}\\
\employer{l}\location{r}\\
\body
\end{format}

\begin{document}
\begin{resume}

\section{SKILLS}
\begin{tabular}{ l l }
Programming Languages: &
Ruby,
Python,
JavaScript,
CSS/Sass,
Erlang,
Haskell,
Bash\\

Tools: &
Rails,
Django,
React,
SQL,
Unix,
Elasticsearch,
Git,
Vim,
Docker,
AWS\\

\end{tabular}

\section {EXPERIENCE}
\vspace {2 pt}

\employer{\textit{Bocoup}}
\title{Tech Lead \& Senior Developer}
\dates{\small {April 2020 - December 2020}}
\location{\small {Remote / Boston, MA}}
\begin{position}
\noindent
\vspace {-10 pt}
\begin{itemize}

\item Led project to build an accessabilty-focused test harness for the W3C.
\item Led greenfield project to build a legal eviction defense tool.
\item Managed project planning to meet long-term goals.
\item Maintained infrastructure with Ansible, AWS, and Terraform.
\item Built, tested, and deployed web applications made with React, Redux, and Express.
\item Triaged, addressed issues, and improved documentation for open source
  projects.

\end{itemize}
\end{position}

\employer{\textit{Context Travel}}
\title{Senior Developer}
\dates{\small {September 2017 - March 2020}}
\location{\small {Remote / New York City, NY}}
\begin{position}
\noindent
\vspace {-10 pt}
\begin{itemize}

\item Built and maintained Rails, Angular, and Backbone apps.
\item Optimized the performance of a complex e-commerce site.
\item Worked closely with product, design, and marketing to increase conversion.
\item Mentored junior developers.
\item Built a tech team with a healthy remote culture.
\item Provided leadership and guidance to determine the technical roadmap.

\end{itemize}
\end{position}

\employer{\textit{Hemnet}}
\title{Backend Developer}
\dates{\small {January 2015 - July 2016}}
\location{\small {Stockholm, SE}}
\begin{position}
\noindent
\vspace {-10 pt}
\begin{itemize}

\item Developed, deployed, and maintained complex Rails and Node applications.
\item Improved uptime and performance for a site with over 2 million visitors per week.
\item Performed dev-ops functions including maintaining Puppet and on-call duties.
\item Added metrics to provide measurable insight into platform characteristics.
\item Contributed patches to our own and third-party open source libraries.
\item Upgraded from Rails 2 to 4 while ensuring uptime.
\item Increased test coverage from 20 to 80 percent.
\item Switched from Oracle to PostgreSQL and Elasticsearch.
\item Collaborated and communicated with other teams to promote developer happiness.

\end{itemize}
\end{position}

\employer{\textit{FundedByMe}}
\title{Lead Developer}
\dates{\small {February 2013 - December 2014}}
\location{\small {Stockholm, SE}}
\begin{position}
\noindent
\vspace {-10 pt}
\begin{itemize}

\item Built Django Web app for an international crowdfunding platform.
\item Worked with Product to prioritize features and triage tickets.
\item Instituted and enforced a culture of automation, CI testing, and code reviews.
\item Conducted technical interviews for the development team.
\item Expanded and managed development team onboarding documentation.
\item Automated deployment process with Fabric, CircleCI, and Heroku.
\item Increased development team transparency via release notes and issue tracking.
\item Published, tested, maintained, and documented open source libraries.

\end{itemize}
\end{position}


\employer {\textit{Klarna}}
\title{Developer}
\dates{\small {May 2011 - January 2013}}
\location{\small {Stockholm, SE}}
\begin{position}
\noindent
\vspace {-10 pt}
\begin{itemize}
\item Designed, developed, and tested secure APIs in Erlang using OTP behaviors.
\item Worked with an agile team on fault-tolerant backend infrastructure for global e-commerce.
\item Communicated and presented to team and key stakeholders.
\item Facilitated the release process including the development of tools.
\item Integrated with external services and open source libraries.
\end{itemize}
\end{position}

\employer {\textit{MIT Lincoln Laboratory}}
\title{Mechanical Engineering Co-op}
\dates{\small {January 2010 - June 2010}}
\location{\small {Lexington, MA}}
\begin{position}
\noindent
\vspace {-10 pt}
\begin{itemize}
\item Designed LASER Optical Module for XPrize competition.
\item Developed and conducted preliminary tests of module components.
\end{itemize}
\end{position}

\employer{\textit {Center for High-Rate Nanomanufacturing}}
\title{Undergraduate Research Assistant}
\dates{\small{June 2008 - December 2009}}
\location{\small{Boston, MA}}
\begin {position}
\vspace {-10 pt}
\begin{itemize}
\item Co-authored: "Engineering Low-Aspect Ratio Carbon Nanostructures: Nanocups, Nanorings, and Nanocontainers," ACS Nano, 2009.
\item Optimized process to grow densely packed, vertically-aligned, single-wall nanotubes.
\item Operated and developed recipes for chemical vapor deposition furnace, ion mill, inductive coupling plasma, electron beam evaporator, and scanning electron microscope.
\end{itemize}
\end{position}

\employer{\textit{Naval Sea Systems Command}}
\title{Torpedo R\&D Engineering Co-op}
\dates{\small {January 2009 - August 2009}}
\location{\small{Washington, D.C./Newport, RI}}
\begin {position}
\vspace {-10 pt}
\begin{itemize}
\item Created expense plans and a process for tracking expend
    pressure vessel tests.
\end{itemize}
\end{position}

\section{EDUCATION}
\vspace {2 pt}

University of British Columbia, Vancouver, BC, Canada\hfill Expected Graduation December 2021\\
Masters of Engineering Leadership in Dependable Software Systems \

Northeastern University, Boston, MA, USA\hfill Graduation April 2011 \\
B.S. Mechanical Engineering, Honors College \hfill G.P.A. 3.76/4.0 \

\end{resume}
\end{document}
